Reproducibility and Open Science in Economics

### 2025-07-13 article.tex

The broader literature has often measured the benefits of open science in indirect measures, through citations, and in more recent studies find some advantages for studies with linked data \citep{piwowar_data_2013,colavizza_citation_2020,christensen_study_2019}.\footnote{Some of these studies need to be taken with a grain of salt, since they typically measure whether data is referenced, not whether it is actually openly available.} The economics literature has emphasized the benefits of (balanced) open science. \citet{nagaraj_improving_2020} discuss the canonical example of improved data access through (free) public-use data in the context of satellite imagery. Patents can be usefully investigated, since they are both openly viewable but also access-limiting by their very nature. Economists have looked at how restrictiveness, duration, and type of patents affect scientific progress. In general, restrictions reduce social welfare \citep{williams_intellectual_2013,murray_mice_2016}, even enabling anti-competitive behavior that directly identify welfare loss \citep{xie_anticompetitive_2020}. The much broader applicability of open science practices is also much more recent, and as of yet, hard to measure. Nevertheless, it appears to be widely accepted in economics, as evidenced by very strong positive attitudes (

>>>>

A different thread in the discussion brings up normative reasons for transparency, for instance around Mertonian \citep{merton1942note} norms of openness

The  benefits of open science have often been measured indirectly, through increased citations, say. Some recent studies find some advantages for studies with linked (openly available) data \citep{piwowar_data_2013,colavizza_citation_2020,christensen_study_2019}.\footnote{Some of these studies need to be taken with a grain of salt, since they typically measure whether data is referenced, not whether it is actually openly available.} The economics literature has emphasized the benefits of (balanced) open science. \citet{nagaraj_improving_2020} discuss the canonical example of improved data access through (free) public-use data in the context of satellite imagery. Patents can be usefully investigated, since they are both openly viewable but also access-limiting by their very nature. Economists have looked at how restrictiveness, duration, and type of patents affect scientific progress. In general, restrictions reduce social welfare \citep{williams_intellectual_2013,murray_mice_2016}, even enabling anti-competitive behavior that directly identify welfare loss \citep{xie_anticompetitive_2020}. The much broader applicability of open science practices is also much more recent, and as of yet, hard to measure. Nevertheless, it appears to be widely accepted in economics, as evidenced by very strong positive attitudes (

### 2025-07-13 outputs/stata_downloads_regional_stats_2024_nochina.tex

% latex table generated in R 4.5.1 by xtable 1.8-4 package
% Thu Jun 26 19:15:58 2025
\begin{table}[ht]
\centering
\begin{tabular}{rlrrr}
  \hline
 & custom\_region & countries & Regional Downloads & Fraction \\ 
  \hline
1 & North America &   3 & 3542643 & 66.58 \\ 
  2 & Europe &  40 & 917962 & 17.25 \\ 
  3 & Rest of Asia &  45 & 531155 & 9.98 \\ 
  4 & Africa &  51 & 170296 & 3.20 \\ 
  5 & Latin America \& Caribbean &  28 & 127390 & 2.39 \\ 
  6 & Australia &   1 & 26901 & 0.51 \\ 
  7 & Rest of Oceania &   5 & 4786 & 0.09 \\ 
   \hline
\end{tabular}
\caption{Regional Statistics for Stata Downloads in 2024 (_nochina)} 
\label{tab:stata_downloads_regional_stats_2024_nochina}
\end{table}

>>>>

% latex table generated in R 4.5.1 by xtable 1.8-4 package
% Fri Jun 27 19:46:23 2025
\begin{table}[ht]
\centering
\begin{tabular}{rlrrr}
  \hline
 & custom\_region & countries & Regional Downloads & Fraction \\ 
  \hline
1 & North America &   3 & 3509194 & 66.58 \\ 
  2 & Europe &  40 & 912383 & 17.31 \\ 
  3 & Rest of Asia &  45 & 521557 & 9.90 \\ 
  4 & Africa &  51 & 168663 & 3.20 \\ 
  5 & Latin America \& Caribbean &  28 & 127078 & 2.41 \\ 
  6 & Australia &   1 & 26703 & 0.51 \\ 
  7 & Rest of Oceania &   5 & 4763 & 0.09 \\ 
   \hline
\end{tabular}
\caption{Regional Statistics for Stata Downloads in 2024 (_nochina)} 
\label{tab:stata_downloads_regional_stats_2024_nochina}
\end{table}

### 2025-07-13 outputs/table_stata-licenses.tex
Added better formatting
Further formatting
adding labels
Updated labeling to be tex-safe
changed order
Adding categories
Adjusting the width

% latex table generated in R 4.3.1 by xtable 1.8-4 package
% Fri Feb  7 16:33:05 2025
\begin{table}[h]
\centering
\caption{Software licensing internationally} 
\begin{tabular}{lrrr}
  \toprule
Country & Average monthly income & Stata license & Percent \\ 
  \midrule
USA & 6704 & 690 & 10 \\ 
  Greece & 1883 & 690 & 37 \\ 
  Vietnam & 343 & 220 & 64 \\ 
   \bottomrule
\end{tabular}
\end{table}

>>>>

% latex table generated in R 4.5.1 by xtable 1.8-4 package
% Sat Jun 28 13:39:13 2025
\begin{table}[h]
\centering
\caption{Software licensing internationally} 
\label{tab:licensecost}
\begin{tabular}{lrrrrr}
  \toprule
Country & Average.monthly.income & Stata.license & Laptop & Percent.license & Percent.laptop \\ 
  \midrule
USA & 6,704 & 690 & 849 & 10.3 & 12.7 \\ 
  Greece & 1,883 & 690 & 934.8 & 36.6 & 49.6 \\ 
  Vietnam & 343 & 220 & 706.6 & 64.1 & 206 \\ 
   \midrule \multicolumn{6}{l}{\textit{Notes:} Amounts in USD as of 2025. Source for Stata license prices: Stata website.\newline Sources for laptop prices: HP.com US and German websites, Shopee.vn for Vietnam.} 
 \bottomrule
\end{tabular}
\end{table}
